Joint Training of Classification and Similarity Models for \\ Intention Detection in Task-specific Chatbot

### 2020-09-10 chatbot_classification/aaai_2021/experiments.tex

  \item \emph{Amazon-670K}, is a customer product review dataset for
  text  classification  task  from  the  extreme  classification repository. The
  complete  dataset  contains 670,091 class labels, 285,176 training samples and
  150,875   testing   samples   \cite{bhatia2016extreme}.  As  each  sample  may
  correspond  to  multiple  class labels, we keep only the first one. We further
  filter  out the class labels that each one is associated with 5 to 15 samples,
  or  reviews,  to  mimic  the  chatbot scenario. From them, we sample 250 class
  labels as well as their samples to form a subset with 1,942 + 716 samples.

>>>>

  \item \emph{Amazon-670K}, is a customer product review dataset for
  text  classification  task  from  the  extreme  classification repository. The
  complete  dataset  contains 670,091 class labels, 285,176 training samples and
  150,875   testing   samples   \cite{bhatia2016extreme}.  As  each  sample  may
  correspond  to  multiple  class labels, we keep only the first one. We further
  filter  out the class labels that each one is associated with only 5 to 15 samples,
  or  reviews,  to  mimic  the  chatbot scenario. From them, we sample 250 class
  labels as well as their samples to form a subset with 2658 samples.
